\cvsection[page1sidebar]{Experience}

\cvevent{Software developer (student job)}{Hylastix GmbH}{Oct 2017 -- Ongoing}{Chemnitz, Germany}

\cvtag{Git}
\cvtag{Scala}
\cvtag{Akka}
\cvtag{Python}
\cvtag{REST}
\cvtag{OpenStack}

\medskip
Hylastix is a consultancy firm and sells enterprise virtualization solutions (private and hybrid clouds) mostly based on OpenStack. They also sell programs that enable the management of VMs in an OpenStack cluster both with a UI and through REST APIs. I was involved in the development of the latter.

\divider

\cvevent{Software developer (student job)}{Siemens AG}{May 2016 -- Sept 2017}{Chemnitz, Germany}
\cvtag{Embedded Systems} \cvtag{C / C++} \cvtag{Perl + RegEx} \cvtag{VBA} 

\medskip
I worked in the development department where the Simatic ET-200SP line of PLCs are developed. My occupation was to extend and improve internal software tools as well as create new ones. My most notable fulfilled tasks were: 

\smallskip
\begin{itemize}
\item Design of an Excel macro to analyze and visualize main memory utilization of a PLC.
\item Implementation of a bare-metal firmware for an ASIC in C.
\end{itemize}

\cvsection{Education}

\smallskip
\cvsubsection{Personal research}

I am a very enthusiastic developer. Enthusiastic in the sense that I am on the internet every day looking to learn more about my craft. Sometimes I pick up a term or a name of some technology and get very curious about it. In such cases I spend days googling and researching the topic until I've figured out how it works, what it's used for, how popular it is etc. Below is a list of such topics. I do not have any practical experience with these technologies but I know what they can do and roughly how they work.

\begin{flushleft}
  \cvtag{Cassandra}
  \cvtag{MongoDB}
  \cvtag{Redis}
  \cvtag{SQL vs NoSQL trade-offs}
  \cvtag{Spark}
  \cvtag{Kafka}
  \cvtag{Flink}
  \cvtag{Reactive system}
  \cvtag{CI/CD}
  \cvtag{DevOps}
  \cvtag{AWS, Azure}
  \cvtag{Code quality} 
  \cvtag{Read a book about design patterns}
  \cvtag{Functional Programming}
  \cvtag{Haskell}
  \cvtag{Rust}
  \cvtag{Kotlin}
\cvtag{Java}

\end{flushleft}

\divider

\cvevent{M.S.\ in Computer Science}{Chemnitz University of Technology}{Oct 2016 -- Ongoing}{}

\cvtag{Hadoop ecosystem}
\cvtag{DBMS \& NoSQL} 
\cvtag{CV, ML, DL} \\
\cvtag{Multicore Programming}
\cvtag{CUDA \& OpenCL}
\cvtag{Embedded Systems}

\medskip
Among other things I wrote a term paper: \emph{Accelerating matrix multiplication utilizing Intel HD integrated graphics processors through OpenCL}. I also did my Bachelor's degree at this university from 2012 to 2016.


% \divider

% \cvevent{B.S.\ in Computer Science}{Chemnitz University of Technology}{Oct 2012 -- March 2017}{}

% Topic of my bachelor's thesis: \emph{Fast simulation of biologically realistic neural networks using MPI}. I enrolled in the Master's program preliminarily while finishing my thesis.
